rang

### 2023-07-21 paper/basel2023_rang/index.qmd
Finalize the slides

---
title: "rang"
subtitle: "(Re)constructing reproducible R computational environment"
author: Chung-hong Chan, David Schoch
institute: GESIS
date: "2023-07-21"
date-format: "YYYY-MM-DD"
footer: "https://chainsawriot.github.io/basel2023_rang"
embed-resources: true
format: fakegesis-revealjs
---

<!-- ## Computational reproducibility -->

<!-- |                        | **Same Data** | **Different Data** | -->
<!-- |------------------------|---------------|--------------------| -->
<!-- | **Same Analysis**      | Reproducible  | Replicable         | -->
<!-- | **Different Analysis** | Robust        | Generalisable      | -->

<!-- ::: {style="font-size: 0.3em"} -->

<!-- Source: [The Turing Way](https://the-turing-way.netlify.app/reproducible-research/overview/overview-definitions.html) -->

<!-- ::: -->

## Computational Reproducibility

@@

<!-- :::: {.columns} -->

<!-- :::{.column width="50%"} -->

<!-- ![](bowie.jpg) -->

<!-- (1947.01.08 - 2016.01.10) -->
<!-- ::: -->

<!-- :::{.column width="50%"} -->

@@

<!-- ::: -->

<!-- :::: -->

@@

```{.r code-line-numbers="|1|2|"}
p3m <- "https://packagemanager.posit.co/cran/2016-01-10"
options(repos = c(REPO_NAME = p3m))
install.packages("dplyr") # install 0.4.3?

@@

```{.r code-line-numbers="|3|"}
require(renv)
renv::init() ## restart
renv::checkout(date = "2016-01-10") 
install.packages("dplyr")
renv::snapshot()
require(dplyr)
data <- data.frame(id = c(1,1,2), outcome = c(TRUE, TRUE, FALSE))
distinct(data, id) %>%
    select(outcome)
```

>>>>

---
title: "rang"
subtitle: "(Re)constructing reproducible R computational environment"
author: Chung-hong Chan, David Schoch
institute: GESIS
date: "2023-07-21"
date-format: "YYYY-MM-DD"
footer: "https://chainsawriot.github.io/basel2023_rang"
embed-resources: true
format: fakegesis-revealjs
---
## Computational Reproducibility

@@

@@

::: {style="font-size: 0.3em"}
Source: [https://dplyr.tidyverse.org/news/index.html#dplyr-050](https://dplyr.tidyverse.org/news/index.html#dplyr-050)
:::

@@

```{.r code-line-numbers="|1,2"}
p3m <- "https://packagemanager.posit.co/cran/2016-01-10"
options(repos = c(REPO_NAME = p3m))
install.packages("dplyr") # install 0.4.3?

@@

```{.r code-line-numbers="|4"}
require(renv)
renv::init() ## restart
install.packages("dplyr")
renv::checkout(date = "2016-01-10")
renv::snapshot()
require(dplyr)
data <- data.frame(id = c(1,1,2), outcome = c(TRUE, TRUE, FALSE))
distinct(data, id) %>%
    select(outcome)
```
